Real Estate

### 2023-01-31 src/anchor_city_real_estate.Rmd
calculated weighted sum

library(tidyverse)
library(janitor)
library(googlesheets4)
library(DT)

@@

anchor_cities_list <- unique(anchor_cities$city_msa)

@@

```{r}
# normalize columns into new data table
n_MSA_realEstate <- compliedMSA_realEstate %>% 
  # normalize population data
  mutate(n_pop_change = (pop_percent_change20_21 - min(pop_percent_change20_21))/(max(pop_percent_change20_21)-min(pop_percent_change20_21))) %>%
  # normalize employment growth
  mutate(n_employ_change = (avg_emp_YoY - min(avg_emp_YoY)) / (max(avg_emp_YoY) - min(avg_emp_YoY))) %>% 
  # normalize rent to income
  mutate(n_med_rent_to_income = (med_rent_to_income- min(med_rent_to_income)) / (max(med_rent_to_income) - min(med_rent_to_income))) %>% 
  # normalize income to home price
  mutate(n_med_rent_change = (med_rent_change - min(med_rent_change)) / (max(med_rent_change) - min(med_rent_change))) %>% 
  mutate(n_income_to_homeprice = (income_to_homeprice - min(income_to_homeprice)) / (max(income_to_homeprice) - min(income_to_homeprice))) %>% 
  mutate(n_avg_occupancy = (occ_rate2021 - min(occ_rate2021)) / (max(occ_rate2021) - min(occ_rate2021)))

@@

for (i in 1:size[1]) {
  MSA_x_data <- c(n_MSA_realEstate$n_pop_change[i],
                  n_MSA_realEstate$n_employ_change[i],
                  n_MSA_realEstate$n_avg_occupancy[i],
                  n_MSA_realEstate$n_med_rent_change[i],
                  n_MSA_realEstate$n_med_rent_to_income_inverted[i], 
                  n_MSA_realEstate$n_income_to_homeprice_inverted[i]
                  )
  n_MSA_realEstate$real_estate_score[i] = weighted.mean(MSA_x_data, real_estate_weights)
}

>>>>

library(tidyverse)
library(janitor)
library(googlesheets4)
library(DT)
library(MCDA)

@@

anchor_cities_list <- unique(anchor_cities$anchor_city)

@@

```{r}
# normalize columns into new data table
n_MSA_realEstate <- compliedMSA_realEstate %>% 
  # normalize population data
  mutate(n_pop_change = (pop_percent_change20_21 - min(pop_percent_change20_21))/(max(pop_percent_change20_21)-min(pop_percent_change20_21))) %>%
  # normalize employment growth
  mutate(n_employ_change = (avg_emp_YoY - min(avg_emp_YoY)) / (max(avg_emp_YoY) - min(avg_emp_YoY))) %>% 
  # normalize rent to income
  mutate(n_med_rent_to_income = (med_rent_to_income- min(med_rent_to_income)) / (max(med_rent_to_income) - min(med_rent_to_income))) %>% 
  # normalize income to home price
  mutate(n_med_rent_change = (med_rent_change - min(med_rent_change)) / (max(med_rent_change) - min(med_rent_change))) %>% 
  mutate(n_income_to_homeprice = (income_to_homeprice - min(income_to_homeprice)) / (max(income_to_homeprice) - min(income_to_homeprice))) %>% 
  mutate(n_avg_occupancy = (occ_rate2021 - min(occ_rate2021)) / (max(occ_rate2021) - min(occ_rate2021)), na.rm = FALSE)

@@

for (i in 1:size[1]) {
  MSA_x_data <- c(n_MSA_realEstate$n_pop_change[i],
                  n_MSA_realEstate$n_employ_change[i],
                  n_MSA_realEstate$n_avg_occupancy[i],
                  n_MSA_realEstate$n_med_rent_change[i],
                  n_MSA_realEstate$n_med_rent_to_income_inverted[i], 
                  n_MSA_realEstate$n_income_to_homeprice_inverted[i]
                  )
  n_MSA_realEstate$real_estate_score[i] = sum(MSA_x_data * real_estate_weights)
}

```{r}

weighted_table <-n_MSA_realEstate %>% 
  mutate(weighted_pop_change = 0.35*n_pop_change,
                  weighted_emp_change = 0.20*n_employ_change,
                  weighted_occ = 0.15 * n_avg_occupancy,
                  weighted_rent_change = 0.10*n_med_rent_change,
                  weighted_rent_income = 0.10 * n_med_rent_to_income_inverted, 
                  weighted_income_homeprice = 0.10 * n_income_to_homeprice_inverted) %>% 
  mutate(real_estate_score = weighted_pop_change + weighted_emp_change + weighted_occ + weighted_rent_change + weighted_rent_income + weighted_income_homeprice)
